Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2022-12-20 paper_comparison/paper_comparison/paper_comparison.Rmd
Cite mpoly and Hermite polynomials

(handbook of mathathetical function, https://aapt.scitation.org/doi/10.1119/1.15378, cite the package)

(hermite poly is created by ... in 18..,)

Experiment I is designed to study the ability of human subjects to detect the effect of a non-linear term $\boldsymbol{z}$ constructed using Hermite polynomials [unsure how to cite 1810 work] on random vector $\boldsymbol{x}$ formulated as

@@

>>>>

<!-- (handbook of mathathetical function, https://aapt.scitation.org/doi/10.1119/1.15378, cite the package) -->

<!-- (hermite poly is created by ... in 18..,) -->

Experiment I is designed to study the ability of human subjects to detect the effect of a non-linear term $\boldsymbol{z}$ constructed using Hermite polynomials [@hermite1864nouveau] on random vector $\boldsymbol{x}$ formulated as

@@

Hermite polynomials were initially defined by @de1820theorie, but named after Hermite [@hermite1864nouveau] because of the unrecognisable form of Laplace's work. When simulating $Z_{raw}$, the function `hermite` from the R package `mpoly` [@mpoly] was used to generate Hermite polynomials.

### 2022-12-20 paper_comparison/paper_comparison/paper_comparison.tex
Cite mpoly and Hermite polynomials

(handbook of mathathetical function,
\url{https://aapt.scitation.org/doi/10.1119/1.15378}, cite the package)

(hermite poly is created by \ldots{} in 18..,)

Experiment I is designed to study the ability of human subjects to
detect the effect of a non-linear term \(\boldsymbol{z}\) constructed
using Hermite polynomials {[}unsure how to cite 1810 work{]} on random
vector \(\boldsymbol{x}\) formulated as

@@

>>>>

Experiment I is designed to study the ability of human subjects to
detect the effect of a non-linear term \(\boldsymbol{z}\) constructed
using Hermite polynomials \citep{hermite1864nouveau} on random vector
\(\boldsymbol{x}\) formulated as

@@

Hermite polynomials were initially defined by \citet{de1820theorie}, but
named after Hermite \citep{hermite1864nouveau} because of the
unrecognisable form of Laplace's work. When simulating \(Z_{raw}\), the
function \texttt{hermite} from the R package \texttt{mpoly}
\citep{mpoly} was used to generate Hermite polynomials.
